weight_analyses

### 2022-11-16 smelt_2019_winterspring/ZoopPlotting.Rmd
updated dataframe name
updated to match new column headers

# load data
```{r}
zoop <- read_csv("smelt_2019_winterspring/data_raw/ZoopDataCombined_biomass_qc'ed_12.19.19.csv")

@@

zoop$RingSize_m <- zoop$RingSize_cm/100

@@

tow$distance<-(tow$Rotations)*26873/999999 #R: Rotor constant (Regular flow = 26873, Low flow = 57560) - used Reg flow meter for this study
tow$volumesampled<-((pi*(tow$RingSize_m^2))/4)*tow$distance
tow$samplecount<-(tow$TotalVolume_ml/tow$Subsampled_ml)*tow$Count
tow$ind_m3<-tow$samplecount/tow$volumesampled

#to incorporate biomass
tow$samplebiomass<-(tow$TotalVolume_ml/tow$Subsampled_ml)*tow$Total.Biomass
tow$bio_m3<-tow$samplebiomass/tow$volumesampled

@@

throw$distance<- "NA"
throw$radius<-throw$RingSize_m/2
throw$volumesampled<- throw$radius*2*pi*throw$TowDistance_m+(2*pi*(throw$radius^2))
throw$samplecount<-(throw$TotalVolume_ml/throw$Subsampled_ml)*throw$Count
throw$ind_m3<-throw$samplecount/throw$volumesampled

#to incorporate biomass
throw$samplebiomass<-(throw$TotalVolume_ml/throw$Subsampled_ml)*throw$Total.Biomass
throw$bio_m3<-throw$samplebiomass/throw$volumesampled
```

# bind throw and tow methods & calcualte species abundance for Table 6
```{r}
#combine
tow$radius<-tow$RingSize_m*2
abundance <- rbind(tow, throw)
abundance$Date<-ymd(abundance$Date)
abundance$Taxa<-as.factor(abundance$Taxa)
abundance$ind_m3<-as.numeric(abundance$ind_m3)

#put together results for Table 6
top.sp<-abundance %>% 
  group_by(SiteName, Taxa, ID) %>% 
  summarize("ind"= sum(ind_m3), "bio"=sum(bio_m3))

@@

#sum by site (to get denominator)
sum<-top.sp %>% 
  group_by(SiteName) %>% 
  summarize("sum"= sum(bio))

#break into DWSC and RV
dw <- top.sp %>% filter(SiteName == "DWSC")
rv <- top.sp %>% filter(SiteName == "RV")

dw$DWSC.Bio <- dw$bio
dw$DWSC.Perc <- (dw$DWSC.Bio/12832.26)*100
dw <- dw[c(2,3,7,8)]
dw2 <- subset(dw, DWSC.Bio!=0)

rv$RV.Bio <- rv$bio
rv$RV.Perc <- (rv$RV.Bio/32782.81)*100
rv <- rv[c(2,3,7,8)]
rv2 <- subset(rv, RV.Bio!=0)

#merge
all <- merge(rv2,dw2,by=c("ID","Taxa"),all=TRUE)

@@

# stacked bar across week plot
```{r}
taxa<-abundance %>% 
  group_by(SiteName, Date, Taxa) %>% 
  summarize("ind"= sum(ind_m3), "bio"=sum(bio_m3))

@@

#zeros already exist, go ahead and average 
taxa.week<-taxa %>% 
  group_by(SiteName, Week, Taxa) %>% 
  summarize("bio.mean"=mean(bio))

@@

ggplot(data = taxa.week, aes(x=Week2, y=bio.mean)) +
  geom_bar(stat = "identity", data=taxa.week, aes (x=Week2, y=bio.mean, fill=factor(Taxa, levels=c("Cladocera", "Calanoid", "Cyclopoid", "Harpacticoid", "Macrozoo", "Microzoo"))), colour="black", width = .5) +
  facet_wrap(~SiteName)+
  theme_bw() + 
    scale_fill_manual(legend_title, values=cbPalette)+theme(axis.title.x = element_blank()) +
  labs(x = "Week") +
  labs(y = "Biomass (ugC/m3)")+
 theme(legend.position="bottom")+theme(axis.text = element_text(size = 20),
        axis.title = element_text(size = 25),
        legend.text = element_text(size = 20),
        legend.title = element_text(size = 25))

@@

taxa.week.2$SiteName = factor(taxa.week.2$SiteName, levels=c('RV','DWSC'))

@@

#plot just macrozoop
z<-ggplot(data = taxa.week.2, aes(x=Week2, y=bio.mean)) +
  geom_bar(stat = "identity", data=taxa.week.2, aes (x=Week2, y=bio.mean, fill=factor(Taxa, levels=c("Cladocera", "Calanoid", "Cyclopoid", "Harpacticoid", "Other"))), colour="black", width = .5) +
    facet_wrap(~SiteName)+
  theme_bw() + 
    scale_fill_manual(legend_title, values=cbPalette)+
  labs(x = "Week") +
  labs(y = "Biomass (ugC/m3)")+
 theme(legend.position="right")+
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size =17),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 17),
        strip.text.x = element_text(size = 17),
        text=element_text(family = "Times"))
z
print(z)

@@

# repeated measures ANOVA
```{r}
#combine taxa 
for.mod<-taxa.week.2 %>% 
  group_by(SiteName, Week, Week2) %>% 
  summarize("bio.all"=sum(bio.mean))

@@

model<-lm(bio.all~SiteName*Week2, data=for.mod)
anova(model)

@@

leveneobject<- lm(abs(resid(model))~SiteName*Week2, data=for.mod)
anova(leveneobject) #insignificant

marginal = emmeans(model, 
                   ~ SiteName*Week2)

>>>>

# load data
```{r}
zoop <- read_csv("smelt_2019_winterspring/data_raw/2019_smeltstudy_zoop_data.csv")

@@

zoop$RingSize_m <- zoop$RingSize/100

@@

tow$distance<-(tow$Rotations)*26873/999999 #R: Rotor constant (Regular flow = 26873, Low flow = 57560) - used Reg flow meter for this study
tow$volumesampled<-((pi*(tow$RingSize_m^2))/4)*tow$distance
tow$samplecount<-(tow$TotalVolume/tow$SubsampledVolume)*tow$Count
tow$ind_m3<-tow$samplecount/tow$volumesampled

#to incorporate biomass
tow$samplebiomass<-(tow$TotalVolume/tow$SubsampledVolume)*tow$TotalBiomass
tow$bio_m3<-tow$samplebiomass/tow$volumesampled

@@

throw$distance<- "NA"
throw$radius<-throw$RingSize_m/2
throw$volumesampled<- throw$radius*2*pi*throw$TowDistance+(2*pi*(throw$radius^2))
throw$samplecount<-(throw$TotalVolume/throw$SubsampledVolume)*throw$Count
throw$ind_m3<-throw$samplecount/throw$volumesampled

#to incorporate biomass
throw$samplebiomass<-(throw$TotalVolume/throw$SubsampledVolume)*throw$TotalBiomass
throw$bio_m3<-throw$samplebiomass/throw$volumesampled
```

# bind throw and tow methods & calcualte species abundance for Table 6
```{r}
#combine
tow$radius<-tow$RingSize*2
abundance <- rbind(tow, throw)
abundance$Date<-ymd(abundance$Date)
abundance$Taxa<-as.factor(abundance$TaxonomicGrouping)
abundance$ind_m3<-as.numeric(abundance$ind_m3)

#write file for use in analysis for another project
write_excel_csv(all, "smelt_2019_allseasons/data_clean/zoop_abundance.csv")

#put together results for Table 6
top.sp<-abundance %>% 
  group_by(Location, Taxa, Taxon) %>% 
  summarize("ind"= sum(ind_m3), "bio"=sum(bio_m3))

@@

#sum by site (to get denominator)
sum<-top.sp %>% 
  group_by(Location) %>% 
  summarize("sum"= sum(bio))

#break into DWSC and RV
dw <- top.sp %>% filter(Location == "DWSC")
rv <- top.sp %>% filter(Location == "RV")

dw$DWSC.Bio <- dw$bio
dw$DWSC.Perc <- (dw$DWSC.Bio/12832.26)*100
dw <- dw[c(2,3,6,7)]
dw2 <- subset(dw, DWSC.Bio!=0)

rv$RV.Bio <- rv$bio
rv$RV.Perc <- (rv$RV.Bio/32782.81)*100
rv <- rv[c(2,3,6,7)]
rv2 <- subset(rv, RV.Bio!=0)

#merge
all <- merge(rv2,dw2,by=c("Taxa","Taxon"),all=TRUE)

@@

# stacked bar across week plot
```{r}
taxa<-abundance %>% 
  group_by(Location, Date, Taxa) %>% 
  summarize("ind"= sum(ind_m3), "bio"=sum(bio_m3))

@@

#zeros already exist, go ahead and average 
taxa.week<-taxa %>% 
  group_by(Location, Week, Taxa) %>% 
  summarize("bio.mean"=mean(bio))

@@

ggplot(data = taxa.week, aes(x=Week2, y=bio.mean)) +
  geom_bar(stat = "identity", data=taxa.week, aes (x=Week2, y=bio.mean, fill=factor(Taxa, levels=c("Cladocera", "Calanoid", "Cyclopoid", "Harpacticoid", "Macrozoo", "Microzoo"))), colour="black", width = .5) +
  facet_wrap(~Location)+
  theme_bw() + 
    scale_fill_manual(legend_title, values=cbPalette)+theme(axis.title.x = element_blank()) +
  labs(x = "Week") +
  labs(y = "Biomass (ugC/m3)")+
 theme(legend.position="bottom")+theme(axis.text = element_text(size = 20),
        axis.title = element_text(size = 25),
        legend.text = element_text(size = 20),
        legend.title = element_text(size = 25))

@@

taxa.week.2$SiteName = factor(taxa.week.2$Location, levels=c('RV','DWSC'))

@@

#plot just macrozoop
z<-ggplot(data = taxa.week.2, aes(x=Week2, y=bio.mean)) +
  geom_bar(stat = "identity", data=taxa.week.2, aes (x=Week2, y=bio.mean, fill=factor(Taxa, levels=c("Cladocera", "Calanoid", "Cyclopoid", "Harpacticoid", "Other"))), colour="black", width = .5) +
    facet_wrap(~Location)+
  theme_bw() + 
    scale_fill_manual(legend_title, values=cbPalette)+
  labs(x = "Week") +
  labs(y = "Biomass (ugC/m3)")+
 theme(legend.position="right")+
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size =17),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 17),
        strip.text.x = element_text(size = 17),
        text=element_text(family = "Times"))
z
print(z)

@@

# repeated measures ANOVA
```{r}
#combine taxa 
for.mod<-taxa.week.2 %>% 
  group_by(Location, Week, Week2) %>% 
  summarize("bio.all"=sum(bio.mean))

@@

model<-lm(bio.all~Location*Week2, data=for.mod)
anova(model)

@@

leveneobject<- lm(abs(resid(model))~Location*Week2, data=for.mod)
anova(leveneobject) #insignificant

marginal = emmeans(model, 
                   ~ Location*Week2)
